Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: Seminars and workshops: Work in progress

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        Internal personnel is coaching  &
                P2, P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 16
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

@@

@@

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 18
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Seminars and public events

What?

Why?

For whom?

Benefit?

@@

Organizations typically strived to increase the agile awareness by events
promoting agile, ranging from public seminars to workshops. These events were
aimed at a general audience, consisting of all organizational groups. Events
were arranged especially in the beginning of the agile journey. In some cases
the demand and interest in public events was maintained, and the events were
continued.

Some cases describe continually arranged agile events [P47].

Organizations took the opportunity to promote the new way of working.

Some organizations productized the training events, so that they could be
replicated for a large number of people [P46].

The ``how things are done here'' attitude was being broken down by conducting
workshops [P16].
Workshops were used to get people better involved [P16].

The purpose of these events was to evangelize and expand the agile model
throughout the organization [P10].

Hands-on workshops were used as a teaching method as they could be made more
engaging than traditional lectures [P32, P41].

Another benefit of open events was that the same message was delivered to many
people at the same time []. As everyone could heard the same questions and
answers the understanding was consistent [P41].

@@

[P1, P2]
* Purpose: Translating agile principles
* What: Special workshops, presentations, events of public recognition eg. agile awards
* For: Rest of business

[P3]
* What: A series of talks
* For: People in the organization
* Benefit: People kept comming back, even if the benefits were not tangible
--
* When: When there was enough interest
* What: Scrum gathering

[P4]
* Purpose: Coordinating activities for increasing knowledge and understanding
* What: Competency day, weekly meetings, seminars and presentations for customers

[P7]
* When: in the beginning
* Purpose: To identify initial problems, practical implementation planning
* What: Workshops
* For: Teams

[P9]
* When: In the beginning
* Purpose: To ignite interest
* What: Agile experts talks, public open sessions
--
* When: During pilots
* What: Practical workshops, real-world examples
* Benefit: They became popular, even outside of pilot teams
* Benefit: Common understanding across the organization
--
* When: Further in the transformation
* What: Agile talks, External agile community events

[P10]
* When: In the beginning, when the agile transformation was on
* What: Lunch sessions, classes in different agile disciplines
* Purpose: To evangelize the agile model

[P11] (?)
* When: In the beginning
* Purpose: To train people
* What: A short introductory presentation

[P16]
* When: During the transformation
* Purpose: To involve individuals better
* What: Workshops to go over the agile way of working, and to identify problems
* Benefit: The workshops should have been used earlier to improve the transformation

[P23]
* When: In the transformation
* What: Agile roadshow, Agile program days, Agile learning projects
* Purpose: Promote awareness, give a one day deep dive, project level engagements
--
* When: Continued
* What: Based on the roadshow, knowledge share events
* Why: Because of the initial interest

[P25]
* When: During the first year
* What: introductory presentation
--
* When: Later
* What: Workshops lead by external speakers

[P26]
* Purpose: To correct people from sidetracks
* What: Public lectures on agile, in all development centers

[P27]
* What: Lunch seminars, open space meetings
* Purpose: To spread domain knowledge
* Purpose: Brainstorm solutions to problems with conslutants

[P32]
* When: Continuous
* What: Joining the dots events, 100 people at a time
* What: Hands-on workshop
* Purpose: Communicate the new ways of working, ensure understanding of agile for everyone
* Benefit: A fun way of learning

[P41]
* When: Kick off for teams
* What: Transition day programme
* For: All teams
* Benefit: All teams could participate, and get a common understanding
* Benefit: Everyone hears the same questions

[P44] (?)
* When: In the beginning
* What: An introductory workshop by an agile consultant

[P46]
* When: During the transformation
* What: A sequence of agile training
* What: Workshops
* Purpose: To set the team straight

[P47]
* What: Two meetings a month
* What: An open meeting for everyone who wants to participate in shaping the agile model
* What: Various agile topics
